Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Updated the diagram to reflect changes of abbreviations.
Moved much of the agreed/disagreed discussion into Section 2.
Finished Section 2 and 3.

\begin{table}
  \centering
  \caption{Stack Overflow and Qualitas datasets}
  \label{tab:datasets}
  \small
  \begin{tabular}{lrr}
    \hline 
    Dataset & No. of files & SLOC \\
    \hline
    Stack Overflow & 144,064 & 2,346,267 \\ 
    %\hline 
    Qualitas &  160,937 & 19,086,883 \\ 
    \hline 
  \end{tabular} 
\end{table}

@@

\subsection{Clone Detection Parameter Tuning}

@@

@@

The number of clones detected in large-scale datasets can be huge. In
our study, there are in total 315,786,118 clone pairs reported. It is
infeasible for humans to manually validate them all. Instead of
investigating a random saple, we adopted the idea of \textbf{clone
  agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow the original definitions of
\textit{good}- and \textit{ok}-match introduced in Bellon's
paper~\cite{Bellon2007}.

@@

\noindent%
Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(t)} iff, for threshold $t \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
\end{equation}
%
Similarly for an \textit{ok-match(t)} pair
%\squeezeup
\begin{equation}
ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
\end{equation}

Using the good and ok-match criteria with a predefined threshold
\textit{t}, we can prune the 315 million candidate clone pairs for
manual investigation. The \textit{good} pairs are the ones with the
highest confidence, followed by the \textit{ok} pairs, and followed by
clone pairs without agreement. We call the \textit{good} and
\textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs
reported by Simian or NiCad without agreement \textbf{disagreed} clone
pairs.

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated \\ 
			\hline 
			IN & Inheritance, interface implementation  \\ 
			\hline 
			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

\subsubsection{The Seven Patterns of Online Code Cloning}

We are interested in the analysis of the patterns of online code clones. We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study. Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet. We selected these four criteria so that we could cover the online clones from various aspects. We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets. The snippets were associated with 697 clone pairs. Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.

The benefit of the study is two-folded. We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs. \textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns . The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow. The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.  Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying. %The UD clones are also unique enough to not be a boiler-plate code. 
Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components. Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface. These two activities usually result in similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs. These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.

%With the online cloning patterns, we could calculate the number of true and false positives. %We are looking for unique and meaningful clones in this study. Thus,

\subsubsection{Classification of Clone Candidates}

@@

The online clone classification follows the steps depicted in \Cref{fig:classification_process}. First, we look at a pair of clone fragments to see their similarity. If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC. If the two fragments are boiler-plate code, the pair is classified into BP. If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN. If the pair is not BP, IN, or AC, we start a detailed investigation. We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying. If evidence of copying has been found from a Qualitas project, the pair is classified in QS. In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding. On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ. If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX. Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.

@@

We used the experimental framework (\Cref{fig:exp_framework}) to
detect clones between Stack Overflow and the Qualitas corpus using the
two selected clone detectors. To answer RQ1, we computed statistics on
discovered clones. To answer RQ2, we manually investigated online
clone pair candidates and categorised them using patterns of online
code cloning. The patterns were derived from Kapser et
al.~\cite{Kapser2003} and augmented by common patterns found in our
data set. For RQ3, we looked at the true positive clone pairs and
checked if they have been changed since they have been
cloned. Similarly, for RQ4, we looked at the license of each
clone and checked for a possibility of a licensing violation.

@@

\begin{table}
	\centering
	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects. We encountered NiCad failures with a few Qualitas
projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
clustering errors. $N_E$ generated errors during code normalisation by 
variable renaming for 5 projects including \textsf{vuze},
\textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
\textsf{spring}. We have contacted the creator of NiCad regarding the
issues. They identified the issues as problems in the TXL grammar and
as problems of long file paths, and will be fixed in the next NiCad
releases.

% \Cref{fig:histogram} illustrates the distribution of online code
% clones reported by $S_D$, $N_D$, $S_E$ and $N_E$ respectively. We can
% see that the distribution is right skewed. There are only a few Stack
% Overflow snippets and Qualitas projects that are outliers containing a
% larger number of clones compared to the others.

In terms of the number of clone pairs, $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.
% Using $S_D$, we found 62 clones in average originating from a single
% Stack Overflow snippet. 62 and 455 respectively. On the other hand,
% $S_E$ and $N_E$ have a much larger number of 63 and 251 million
% clone pairs per snippet on average.
The average clone size reported by $S_D$ is 9.11 lines which is bigger
than for $S_E$ (5.95 lines). Similarly, $N_D$ has an average clone
size of 10.85 lines which is bigger than 6.28 lines reported by
$N_E$. The drop in size is due to the EvaClone configuration with a
smaller minimum size (\Cref{t:param_tuning}). For the cloned Stack
Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$,
$N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

% FIXME
% However, as it is well known that the precision of clone detectors is
% not very good, it is clear that the above numbers may not be
% representative for real code clones and we ...

@@

We rely on a manual study to qualitatively investigate the patterns of online code cloning. To achieve this, we select a subset of the agreed clones using Bellon's criteria and a subset of the disagreed clones using clone filtering. We explain them in more detail below.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
Due to NiCad's failures, we do not have NiCad clones from five Qualitas projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Unique \\
		\hline
		\textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
		\hline
	\end{tabular} %
%}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{Stack Overflow and Qualitas datasets}
  \label{tab:datasets}
  %\small
  \begin{tabular}{lrr}
    \hline 
    Dataset & No. of files & SLOC \\
    \hline
    Stack Overflow & 144,064 & 2,346,267 \\ 
    %\hline 
    Qualitas &  160,937 & 19,086,883 \\ 
    \hline 
  \end{tabular} 
\end{table}

@@

\subsection{Clone Detection Configuration}

@@

We encountered NiCad failures with a few Qualitas projects.~$N_D$
could not detect clones in \textsf{hibernate} due to clustering
errors. $N_E$ generated errors during code normalisation for 5
projects including \textsf{vuze}, \textsf{hibernate},
\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
contacted the creator of NiCad regarding the issues. They identified
the issues as problems in the TXL grammar and as problems of long file
paths, and will be fixed in the next NiCad releases.

@@

The number of online clone pairs reported by running Simian and NiCad
are presented in \Cref{tab:raw_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

\begin{table}
  \centering
  \caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
  \label{tab:orig_stats}
  %\small
  %\resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|r|r|r|r}
      \hline
      Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
      \hline
      Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
      % Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
      Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
      \hline
    \end{tabular} %
  %}
\end{table}

As there are in total 315,786,118 clone pairs reported, it is
infeasible for humans to manually validate them all. Instead of
investigating a random saple, we adopted the idea of \textbf{clone
  agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow the original definitions of good-
and ok-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

\noindent%
Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$
are called a \textit{\textit{good-match}(t)} or \textit{ok-match(t)}  iff, for threshold $t \in [0,1]$ holds 
%\squeezeup
\begin{align*}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t\\
ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t
\end{align*}

Using the good- and ok-match criteria with a predefined threshold
\textit{t}, we can prune the 315 million candidate clone pairs for
manual investigation. The \textit{good} pairs are the ones with the
highest confidence, followed by the \textit{ok} pairs, and followed by
clone pairs without agreement. We call the \textit{good} and
\textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs
reported by Simian or NiCad without agreement \textbf{disagreed} clone
pairs.

@@

As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,308 and the number of \textit{ok}
clone pairs is 31,729, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

\begin{table}
  \centering
  \caption{Distribution of the agreed clone pairs}
  \label{t_agreed_good_clone_pairs}
  %\small
  %	\resizebox{\columnwidth}{!}{%
  \begin{tabular}{l|r|r|r|r|r}
    \hline
    Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
    \hline
    \textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
    \textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
    \hline
  \end{tabular} %
  % }
\end{table}

The distribution of \textit{good} clone pairs between the four
combinations of \textit{D} and \textit{E} configurations are listed in
\Cref{t_agreed_good_clone_pairs}.  There are 2,321 (2,308 unique)
\textit{good} pairs consisting of 18 pairs from $S_D$--$N_D$, 26 pairs
from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
$S_E$--$N_E$. There are 32,560 (31,729 unique) \textit{ok}
pairs\footnote{This excludes the subsumed 2,308 \textit{good}
  pairs. According to the definition, \textit{ok} pairs always subsume
  \textit{good} pairs.}. We obtained 11,467; 993; 79; and 20,021 pairs
from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
respectively. Between the four configuration sets, there is
considerable amount of clone pairs shared between two adjacent sets
(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
that is agreed by all four combinations.

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{M} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\hline
%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{M}=irr.~methods, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

The disagreed clone pairs are clone pairs that are reported by a
single tool, either Simian or NiCad, and do not have agreement with
the other tool. The disagreement can be from a misalignment of clone
lines or completely non-overlapping clones. The disagreed pairs from
Simian include clone pairs in the projects with NiCad's errors (1
project from $N_D$ and 5 from $N_E$).  With the four configuration
combinations, we decided to investigate only $S_D$, and $N_D$, and
dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs
(60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain
a large number of false positives due to the recall preference of
their EvaClone configurations.

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: clone
size, irrelevant methods, similarity threshold, and good/ok pairs. For
the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The \emph{irrelevant methods filter} removes clones of
\verb|hashCode()| methods and getters/setters which are almost always
false clones. The third filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. The last filter, \emph{good/ok pairs}, removes the
clone pairs that already exist in the agreed clone sets.

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
results using clone size, irrelevant methods, and gook/ok pairs. The
three filters reduced the number of $S_D$ clones to 17,801 pairs.  We
filtered $N_D$ clones by additionally raising the similarity
threshold. We increased NiCad's similarity threshold from 70\% to 85\%
(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
85\% similarity provided the best balance in terms of the amount of
reported clones and precision for small clones. Using this filter
along with the other three filters, we reduced the number of $N_D$
clones to 88 pairs.

\subsubsection{Manual Inspection Data Set}

For the manual inspection of clone pairs, we selected all
\textit{good} pairs (2,308) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (11,749), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.

Together with the 17,801 (referred as $S_D'$ set) and 88 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 31,946 online clone pair candidates
for manual inspection.

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c@{~~}p{7.35cm}}
			\hline 
			Patt. & Description \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\

			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\

			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated \\

			IN & Inheritance, interface implementation  \\

			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	%}
\end{table}

\subsection{The Seven Patterns of Online Code Cloning}

As we are interested in the patterns of online code clones, we studied
the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. Using the $S_D$ clone report,
snippets were ranked according to (1)~clone pair frequency,
(2)~popularity (i.e.~number of associated Qualitas projects),
(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
selected these four criteria so that we could cover the online clones
from various aspects. We selected the top 10 from each ranking and
obtained 34 unique Stack Overflow snippets. The snippets were
associated with 697 clone pairs. Using Kapser's cloning patterns, the
clone pairs were categorised into either Customisation or Templating.
However, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.

Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
containing boiler-plate code of {\small\verb|equals()|} methods,
getters/setters, or IDE-generated code such as GUI components. Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

@@

The classification of all 31,946 online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a
pair of clone fragments to see their similarity. If they are
accidentally similar clones after code normalisation or false positive
clones from the clone detection tools, we classify the pair into
\textbf{AC}. If the two fragments are boiler-plate code, the pair is
classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the
pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
check the corresponding Stack Overflow post, read through it carefully
and look for any evidence mentioning code copying. If evidence of
copying has been found from a Qualitas project, the pair is classified
in \textbf{QS}. In several occasions, we used extra information such
as questions' contents, name of posters, and tags to gain a better
understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified
into \textbf{SQ}. If there is evidence of copying from an external
source instead of a Qualitas projects, the pair is classified into
\textbf{EX}. Lastly, if there is no evidence of copying in any
direction but the clone fragments are highly similar, we classify them
into \textbf{UD}.

@@

We used the experimental framework (\Cref{fig:exp_framework}) to
detect clones between Stack Overflow and the Qualitas corpus using the
two selected clone detectors. To answer RQ1, we computed statistics on
discovered clones. To answer RQ2, we manually investigated online
clone pair candidates and categorised them using patterns of online
code cloning. For RQ3, we looked at the true positive clone pairs and
checked if they have been changed since they have been
cloned. Similarly, for RQ4, we looked at the license of each clone and
checked for a possibility of a licensing violation.

@@

\begin{table}
	\centering
	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
%			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
%			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
			\hline
		\end{tabular} %
	%}
\end{table}

@@

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations.

\FIXME{Can you say something about the numbers only looking at the set
  of pairs used for manual inspection?}
% FIXME
% However, as it is well known that the precision of clone detectors is
c% not very good, it is clear that the above numbers may not be
% representative for real code clones and we ...

@@

\begin{table}
	\centering
	\caption{No.~of online clones candidates for the classification}
	\label{tab:online_clone_classification_results}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
		& & Auto & Manual \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
		\multirow{1}{*}{\textit{ok'}} & 11,749 & 11,494 & 255 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
		\multirow{1}{*}{$N_D'$} & 88 & 10 & 78 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

\FIXME{Why equals here but not hashcode? Why isn't it the same
  irrelevant methods filter?}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we used the irrelevant method filter to automatically
classify {\small\texttt{equals()}} and the remaining
getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us classified and captured 28,314 clone pairs into
pattern \textbf{BP}.

There were 3,632 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,632 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.
